\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[ignorenonframetext,]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
\usetheme[]{metropolis}
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Topics in the syntax of ellipsis},
            pdfauthor={Patrick D. Elliott},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\newif\ifbibliography
% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
\centering
\begin{beamercolorbox}[sep=16pt,center]{part title}
  \usebeamerfont{part title}\insertpart\par
\end{beamercolorbox}
}
\setbeamertemplate{section page}{
\centering
\begin{beamercolorbox}[sep=12pt,center]{part title}
  \usebeamerfont{section title}\insertsection\par
\end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
\centering
\begin{beamercolorbox}[sep=8pt,center]{part title}
  \usebeamerfont{subsection title}\insertsubsection\par
\end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usefonttheme[onlymath]{serif}
\input{../common/fontSetup.tex}
\input{../common/lingMacros.tex}
\input{../common/extraPackages.tex}
\usepackage[bibstyle=biblatex-sp-unified,citestyle=sp-authoryear-comp,language=auto,sorting=nyt,maxcitenames=3,maxbibnames=99,natbib=true,autocite=plain,isbn=false,doi=false,url=false,hyperref=auto,uniquename=false,uniquelist=false]{biblatex}
\addbibresource{main.bib}

\title{Topics in the syntax of ellipsis}
\author{Patrick D. Elliott}
\date{25.06.2018}

\begin{document}
\frame{\titlepage}

\hypertarget{class-1-sluicing-and-silent-structure}{%
\section{Class 1: Sluicing and silent
structure}\label{class-1-sluicing-and-silent-structure}}

\begin{frame}{%
\protect\hypertarget{overview}{%
Overview}}

\begin{itemize}
\tightlist
\item
  This class is about the syntax of \emph{ellipsis}.
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{ellipsis}{%
Ellipsis}}

\begin{itemize}
\item
  In \emph{elliptical constructions}, linguistic material is left
  unpronounced, but is nevertheless understood.
\item
  Ellipsis is therefore a classical example of a \emph{form-meaning
  mismatch}.
\item
  Some canonical examples of ellipsis (some of which we’ll be covering
  in this class).

  \begin{enumerate}
  [(1)]
  \item
    \emph{Sluicing}\\
    Someone stayed out until 7am,\\
    but I have no idea who \elide{stayed out
    until 7 am}.
  \item
    \emph{VP ellipsis}\\
    Elin stayed out until 7am, and Fraser did
    \elide{stay out until 7 am} too.
  \item
    \emph{Fragment answers}\\
    Q: Who stayed out until 7am?\\
    A: Elin \elide{stayed out until 7am}
  \end{enumerate}
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{ellipsis-ii}{%
Ellipsis ii}}

\begin{itemize}
\item
  Some other phenomena which have been (controversially) analysed as
  ellipsis:

  \begin{enumerate}
  [(1)]
  \setcounter{enumi}{3}
  \item
    \emph{Comparative deletion}\\
    Fraser stayed out later than Elin \elide{stayed out}.
  \item
    \emph{Pronouns}\\
    A woman walked in. {[}She\(_{\text{D}}\) \elide{woman}{]} sat down.
  \item
    \emph{Conjunction reduction}\\
    Patrick talked to Elin and \elide{Patrick talked to} Fraser.
  \end{enumerate}
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{ellipsis-iii}{%
Ellipsis iii}}

\begin{itemize}
\item
  Ellipsis should be distinguished from other phenomena where linguistic
  material is missing but nevertheless understood, such as,
  e.g.~implicature.

  \begin{enumerate}
  [(1)]
  \setcounter{enumi}{6}
  \tightlist
  \item
    Fraser danced with some of the people at the party.\\
    \(\rightsquigarrow\) \emph{Fraser danced with some of the people at
    the party and he didn’t dance with all of the people at the party}
  \end{enumerate}
\item
  Here, what is \emph{understood} deviates from what we would expect
  based on the compositional semantics.
\item
  There is little to suggest that there was ever a stage in the
  derivation at which this linguistic material was present, however.
\item
  Elliptical phenomena display a distinct signature: the syntax betrays
  that the linguistic material is \emph{missing}, and the missing
  material must be \emph{recoverable} based on the context of utterance.
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{non-recoverable-deletion}{%
Non-recoverable deletion}}

\end{frame}

\begin{frame}{%
\protect\hypertarget{terminology}{%
Terminology}}

\begin{center}
\begin{forest}
[{TP}
    [{Elin}]
    [{T'}
        [{T\\-ed}]
        [{VP},tikz={\node [draw,red,fit=()(!1)(!ll)] {};}
            [{dance}]
            [{PP} [{until 7 am},roof]]
        ]
    ]
]
\end{forest}
%
\begin{forest}
[{TP}
    [{Fraser}]
    [{T'}
        [{T\\did}]
        [{VP},tikz={\node [draw,dashed,fit=()(!1)(!ll)] {};}
            [{dance}]
            [{PP} [{until 7am},roof]]
        ]
    ]
]
\end{forest}
\end{center}

\begin{itemize}
\item
  \textcolor{red}{A(ntecedent)}
\item
  \dashuline{E(llipsis) site}
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{three-questions}{%
Three questions}}

\begin{itemize}
\tightlist
\item
  The \emph{structure} question
\item
  The \emph{identity} question
\item
  The \emph{licensing} question
\end{itemize}

See \textcite{merchant2018}.

\end{frame}

\begin{frame}{%
\protect\hypertarget{the-structure-question}{%
The structure question}}

\begin{enumerate}
[(1)]
\setcounter{enumi}{7}
\tightlist
\item
  In elliptical constructions, is there syntactic structure that is
  unpronounced?
\end{enumerate}

\end{frame}

\begin{frame}{%
\protect\hypertarget{the-identity-question}{%
The identity question}}

\begin{enumerate}
[(1)]
\setcounter{enumi}{8}
\tightlist
\item
  What is the relationship between the understood material and its
  antecedent?
\end{enumerate}

\end{frame}

\begin{frame}{%
\protect\hypertarget{the-licensing-question}{%
The licensing question}}

\begin{enumerate}
[(1)]
\setcounter{enumi}{9}
\tightlist
\item
  What heads or structures allow for \emph{ellipsis}, and what are the
  locality conditions on the relation between these structures and
  ellipsis?
\end{enumerate}

\end{frame}

\begin{frame}{%
\protect\hypertarget{the-identity-and-licensing-conditions}{%
The identity and licensing conditions}}

\begin{itemize}
\item
  \emph{The identity question}\\
  To what extent must an elided constituent be identical to its
  antecedent? At what level is the identity condition enforced – the
  narrow syntax, the semantics, or some other level?
\item
  \emph{The licensing question}\\
  What are the \emph{syntactic licensing conditions} governing ellipsis
  (not everything \emph{recoverable} can necessarily be elided). Can
  only syntactic constituents be elided?
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{guess-who}{%
Guess who!}}

\begin{itemize}
\tightlist
\item
  Since \textcite{Ross}
\end{itemize}

\begin{enumerate}
[(1)]
\setcounter{enumi}{10}
\tightlist
\item
  guess who Δ.
\end{enumerate}

\end{frame}

\begin{frame}{%
\protect\hypertarget{terminology-1}{%
Terminology}}

\end{frame}

\begin{frame}[allowframebreaks]{Bibliography}
\bibliographytrue
\printbibliography[heading=none]
\end{frame}

\end{document}
